Structuring College Access

### 2025-02-08 index.qmd
update TOC

---
title: 'Structuring College Access'
subtitle: 'The Market Segment Model and College Board Geomarkets'
author:
  - name: Ozan Jaquette
    affiliation: UCLA
  - name: Karina Salazar
    affiliation: University of Arizona
  - name: Crystal Han
    affiliation: Stanford University
bibliography: ./assets/bib/cb_geomarket_bib.bib
format:
  revealjs: 
    theme: [default, ./assets/css/custom.scss]
    controls: true
    controls-layout: bottom-right
    controls-tutorial: true
    transition: slide
    background-transition: fade
    auto-stretch: false
    slide-level: 3
    template-partials:
      - ./assets/html/title-slide.html
include-in-header: ./assets/html/header.html
---

@@

### Level-3 heading
#### Level-4 subheading

@@

@@

      # Each metro has 2 plots: "race" & "ses"
      for (g in graph_types_rq1) {
        writeLines(str_c("### Research question ", rq_num))
        insert_figure(rq = rq, metro = m, graph_type = g)
      }

@@

      # We'll do 2 group types: race & firstgen
      for (g in c("race", "firstgen")) {

@@

          if (rc == "row") {
            #
            # ROW => single combined figure on one slide
            #
            writeLines(str_c("### Research question ", rq_num))
            graph_type_row <- str_c(g, "_", rc, "_plot")
            insert_figure(rq = rq, metro = m, graph_type = graph_type_row)

@@

              # Each order ID gets its own "###" => new Reveal.js slide
              writeLines(str_c("### Research question ", rq_num))

@@

      # -------------------------------------------
      # ADDITIONAL: race_by_firstgen for each order
      # -------------------------------------------
      # Like the column approach, one slide per order_id
      for (order_id in orders_for_m) {
        writeLines(str_c("### Research question ", rq_num))
        # Filenames look like:
        #   rq2_northern_new_jersey_order_448922_race_by_firstgen.png
        graph_type_rbf <- str_c("order_", order_id, "_race_by_firstgen")
        insert_figure(rq = rq, metro = m, graph_type = graph_type_rbf)
      }

>>>>

---
title: 'Structuring College Access'
subtitle: 'The Market Segment Model and College Board Geomarkets'
author:
  - name: Ozan Jaquette
    affiliation: UCLA
  - name: Karina Salazar
    affiliation: University of Arizona
  - name: Crystal Han
    affiliation: Stanford University
bibliography: ./assets/bib/cb_geomarket_bib.bib
format:
  revealjs: 
    theme: [default, ./assets/css/custom.scss]
    controls: true
    controls-layout: bottom-right
    controls-tutorial: true
    transition: slide
    background-transition: fade
    auto-stretch: false
    slide-level: 3
    menu:
      titleSelector: 'h1, h2, .slide:not(.hide) h3'
      useTextContentForMissingTitles: false
      hideMissingTitles: true
    template-partials:
      - ./assets/html/title-slide.html
include-in-header: ./assets/html/header.html
---

@@

### Level-3 heading {.hide}
#### Level-4 subheading

@@

# For RQ2, we have two plot types: "race" and "firstgen"
graph_types_rq2 <- c("race", "firstgen")

@@

      # Each metro has 2 plots: "race" & "ses"
      for (i in seq(graph_types_rq1)) {
        g <- graph_types_rq1[i]

        writeLines(str_c("### Research question ", rq_num, if_else(i == 1, "", " {.hide}")))
        insert_figure(rq = rq, metro = m, graph_type = g)
      }

@@

      # We'll do 2 group types: race & firstgen
      for (i in seq(graph_types_rq2)) {
        g <- graph_types_rq2[i]

@@

          if (rc == "row") {
            #
            # ROW => single combined figure on one slide
            #
            writeLines(str_c("### Research question ", rq_num, if_else(i == 1, "", " {.hide}")))
            graph_type_row <- str_c(g, "_", rc, "_plot")
            insert_figure(rq = rq, metro = m, graph_type = graph_type_row)

@@

              # Each order ID gets its own "###" => new Reveal.js slide
              writeLines(str_c("### Research question ", rq_num, " {.hide}"))

@@

      # -------------------------------------------
      # ADDITIONAL: race_by_firstgen for each order
      # -------------------------------------------
      # Like the column approach, one slide per order_id
      for (order_id in orders_for_m) {
        writeLines(str_c("### Research question ", rq_num, rq_num, " {.hide}"))
        # Filenames look like:
        #   rq2_northern_new_jersey_order_448922_race_by_firstgen.png
        graph_type_rbf <- str_c("order_", order_id, "_race_by_firstgen")
        insert_figure(rq = rq, metro = m, graph_type = graph_type_rbf)
      }
